

Thinks I have to remember or be sure about:
-Why do you not reweight the muons pt in the iterative procedure.
-How are the erros of the efficiency moments caculated.
-Make sure you understand the models used in the Kpi mas dependence
-Why the oscilation damping parameter kappa in the production assymetry looks the way it does
-Why no systematic in the detection asymmetry.
-When is a matrix invertible
-Have a genral idea on the transversity framework
-Understand the convension on the signs of production and detection assymetry.
-Why is the efficiency ratio between jpsiphi and jpsikst around two.
-Make sure you know what the p value and chi2 probability is.
-Make sure you know how the luminosity of the mc is scaled to the one of the data.
-nll scans:
    In deltaS1 and deltaS4 the correspondint fS hits upper and lower boundaries.
    In f0 lo stats spiekes. Not there with Bd.
-toys:
    mkpi bin phase and fraction are fine. the gaussian is choped because fS3 is close to a physical boundary. A gaussian pull is not appropriate.
-Acceptance is at the 2 sigma level the same between bs and bd
- Understan why your ang acc systematic is smaller than in the offcial analysis.
- Make sure you knwo what CLT is about.
- Make sure you understand the systematics table of the Br measurement
- understand swave paramterization in the csp factors.

- What is a left/right handed spinor. How dows handedness relates to the V-A nature of the weak interaction
- Why Yuakawa is of the type u_L d_R whereas the CC u_L u_L
- Check all the formulas in the theoretical introduction.
- Why not overconstrain CKM elements in the A,lamda plane?? (cpv does not manifest there.)
- Why wolfenstein is an approximate parametreization.
- Why do we diagonalize the mass matrix in the yukawa couplings.
- The falvour eighestets interact with the materals of the detector?? Noooo
  It is EM responsible for energy loss and decay. (Now what happens with decays in flight.? Like one meson to another)
- Does off-shell mean that the particle exists within heisenberg's uncertainty.??
- Why arent we use the Acp mix and dir form jpsiphi in the penguin fit??
- Why not a use A delta gamma in the penguin fit (maybe it offers little info in the fit)
- Readundant quark phases in the number of ckm parameters.
- The high uncertainty in hadronic parameters is because you ignore correlations between the hadronic forma factors, ncesessary to buuild A/A
- Color supression  explained in krystof page 20
- Low energy effective hamiltonian for B mesons are analogous to the fermi dewcay, which is a 4 point interaction. The W is highly virtual because of the b mass.
- What is facrtorization. What is being factorized )Krystof page 26 (For me it means that quarks seperate before they interact with eachother with gluons)
- Why the hadronic facrtors do not enter the acp mix and acp dir observables.
- What exactly does the wmega-phi mixing affects.(which obesrvables or does the amplitude structure change.??)  maybe check in  {Faller:2008gt}
- more su 3 breakig in hep-ph/9504326
- Be sure of what you write in hadronic paramters section.
- Why C is not Acpmix according to theory.
- Why the sWeights change the likelihood shape. And why, intuitivelly, the errros are underestiamted.
- Why do we quote only statistical uncertainty in the detection assymetry.
-- Make sure you understand the chiw probability in the eff moments tables.
-- Why does the pion not oscilate.
-- Why is the itnerference stronger in Bs wrt the Bd
-- Why one group of toys is bad.
-- What is the physical meaning of a particle that has the space like and time like components equal.
-- What does tuning of the z focal plane and magnet hit erros mean in the matchvelomuon upgrade
-- Why fo you need the intermediate gaussian step in the horizontal reweighitng.
-- Why one ove the angular \pdf integral gives you the acceptance shape in MC.
-- what do the su3 su2 u1 symmetries are ??
-- what is the hierarchuy problem and how is it solved by supersymetry.
-- exampleof an inclusive and what is an exclusive measuremnt
-- why penguin topologies are supressed??
-- Why the mass sideband is nto affectedw by imperfect simulation, selection section
-- why stronger interference in the Bs comapred to the Bd
-- Why the observables ACPdir Acpmix have the shape they have in the real imaginary plane (why unit circle).
-- Whu jpsi rho constrains better the phis (with su3) comapred to jpsiphi
-- Why Brtheo / Brexp is different for odd even and flavor specific.
-- su3 breaking factor delta, why the phase from 0 to 40 and not,. ...blah.
-- B(Bs->J/psiphi) is normalised wrt to B+dJpsiK+ from Babarr and Belle. BdJpsiKst is measured absolutelly from Belle

--Nice comment from Diego: +Page 9: "Testing the unitarity...is a central goal"... To me it is not central anymore after the discovery
of the higgs and the measurement of its couplings. To departure from unitarity, you need new quark
generations with their corresponding Yukawa couplins. But fair enough.
 Also, in the same page, I'm not sure wether Wolfenstein is a good parameterization for unitarity tests,
given the current level of accuracy. Neglecting high orders of \lambda gives a systematic bigger than
the experimental accuracy.


Before printing:
-- Hunt dead refs ??
-- Check position of plots and tables wrt the text
-- Check words going out of the margins.
-- Save lines by rewritting
-- Check for space before \cite{} or not??? ( grep -rG  '[a-zA-Z]\\cite' )
-- Same bibliography layoout for techreports.
-- Spell check:  Use US eng spelling  later --> latter, flavour --> flavor, peaking --> reflection, weather wether ??,

Todo (in order):
-- Robet's coomments
-- Auke-Pieter's comments
-- Diego's comments
-- event display (send to ben blah and boleck, fix colors of the pv sv blobs)
-- translate summary
-- VU layout
-- cover
-- Contact print shop
-- ISBN

Diegos comments:
-- Chapter 1:
  +Fig 1.4: Not sure \bar{ρ} and \bar{η} have been defined.
  +Eqn 17 is very misleading. That is not the \phi_s we use in the fit, but rather its
          SM prediction. (and then you can remove the ^{eff} in Eqn 1.25)
  - Yes. This is what I want to show here, the sm prediction. I do not want to go into
          details of the phis measurement. The thesis is not about phis I think the usual definition \phi_s = arg(q/p \bar{A}/{A}) reflects better what we do.
-- Chapter 2 (will not implement)
  +Page24: Maybe it is worth mentioning the correlation of the b and \bar{b} flight directions,
           which tells you that if you reconstructed one inside LHCb, you have serious chances to reconstruct the other too.
  +Page 25, footnote 1: "quarks" --> "valence quarks"
