
% Chapter 2
\chapter{The \lhcb Detector}
\label{lhcb_detector}
\input{Chapters/Chapter_2_files/intro}

\section{Tracking Systems}
\label{det_tracking}
\input{Chapters/Chapter_2_files/tracking}

\section{Particle Identification}
\label{det_pid}
Two particle identification, PID, systems are used in \lhcb to increase the purity of the analysed data.
The \kaon and \pion are a typical pair that are commonly mis-identified in the absence of partice
identification. Furthermore a particle that is not stoped by the calorimeters is most likely identified
as a muon, since muons can penetrate the entire \lhcb detector without decaying. There are two
{\it Cherenkov} based PID sub-detectors in \lhcb, namely \richone and \richtwo, each one performing
better for low and high momentum tracks respectivelly. The pid effieciencies are shown in the table \tabref{}

\begin{itemize}
  \item Electron ID  90 % for ~ 5 % e→h mis-id probability
  \item Kaon ID 95 % for ~ 5 % π→K mis-id probability
  \item Muon ID 97 % for 1-3 % π→μ mis-id probability
\end{itemize}

\section{Calorimetery}
\label{det_calo}
Calorimeters in \lhcb measure the energy of neutral particeles, for example photons or \piz,
as this type of particles are undetectable by the trackig system. There are four relevant sub-detectors
that enable proper calorimetry at \lhcb. First the combination of the {\it Scintilating Pad Detector} \spd
and the {\it Pre Shower} detector with a led layer in-between them enables to distinguish hadrons from
photons\footnote{and photons from electrons, which leave the same signature in the subsequent electromagnetic calorimeter.}.
Subsequently the electromagnetic, \ecal, and hadronic, \hcal, calorimeters measure the energy of photons
and neutral hadrons respectively. The calorimeter systemt is not expliitly used in the analysis of \chapref{Data_Analysis}.
However, they are implicitly relevant since information from the \spd and \ps sub-detectors are used
by the \lzero trigger system to roughly estimate the energy of an overall event. Furthermore, the
led material that is interlayerd between the \ecal and \hcal active detector material, stops\footnote{Stop here
means that the particle decays and all its decay products are contained inside the calorimeter volume.} most of
the hadrons and thus preventing them from interacting with the muon system. This reduces the chance
of mis-identifing a hadron for a muon, as it was also explained in \secref{det_pid}.

\section{The trigger system}
\label{det_trigger}
\input{Chapters/Chapter_2_files/trigger}

% \section{Favour Tagging}
% \label{det_tagging}
%
% Several important analysis in \lhcb have the feature that either of the initial \B or \Bbar messons
% can decay to the same final state $f$. A typical example is the \BsJpsiPhi decay that is used to
% measure the weak phase \phis, mentioned in \secref{}. In this analsys the precition of the \phis
% measurement increases when the exact flavor of the initial particle is known\footnote{meaning wheather
% the inital particle was a \Bs or \Bsbar, see also \secref{measuring_phis}}. Thus \lhcb has developed
% several {\it flavor tagging} algorithms, \cite{}.

\section{The \BJpsiKst Decay in \lhcb}
\label{BspsiKst_at_lhcb}
\begin{itemize}
  \item Production of \Bs mesons (how many),
  \item Estimate of the expected yield
  \item Event display
  \item Maybe define observables
\end{itemize}
