% Chapter 1

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% Introduction %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\chapter{Introduction}
\label{Introduction}

The main focus of the current thesis is to provide the required ingredients for a high precision measurement of
the weak phase \phis. The latter is an important parameter related to \CP violation, which, as explained throughout
the current chapter, is related to the matter-antimatter asymmetry in the universe. Measuring \phis enables one to look
for deviations from the established theory of elementary particles. Given the state of the art measurement of \phis \cite{phis-3fb-paper},
it is clear that in order to probe potential deviations, \phis needs to be measured with increased precision.
However, entering this high precision regime one finds out that there are sub-leading contributions that need to be
controlled first. Unless this is achieved, a high precision measurement of \phis can not provide insight on possible
deviations. While measuring \phis is based on the analysis of \BsJpsiPhi decays, controlling these sub-leading contributions
requires a different decay channel, like \BsJpsiKst, which plays the role of a control channel. The reason for this becomes apparent in \secref{jpsiphi_amp_struct}.
Essentially, estimating these contributions is more precise when using \BsJpsiKst instead of \BsJpsiPhi decays,
as their effect is enhanced in the former.

The current chapter places \phis into perspective with respect to the established theory of particle physics.
\chapref{lhcb_detector} introduces the \lhcb detector. The analysis of the \BsJpsiKst decays that are
required to control the above mentioned higher order effects is presented in \chapref{Data_Analysis}.
The interpretation and impact of the analysis can be found in \chapref{Penguins}.
Lastly, \chapref{Muon_id_hlt} is dedicated to a particular part of the \lhcb data acquisition system,
which is responsible for selecting a certain type of elementary particles called {\it muons}, see \tabref{quarksLeptons}.
Note that the latter particles are a necessary ingredient for the measurements of \phis and
the analysis of \BsJpsiKst decays.

Finally, the work described in \chapref{Data_Analysis} resulted in the analysis of the \BsJpsiKst
decays \cite{bsjpsikst-paper}, and contributed to the \phis measurement \cite{phis-3fb-paper}.
The work performed in \secref{mvm_algorrithm} is an essential part of the muon identification
software update \cite{Albrecht:2253050} of the \lhcb detector in preparation for the \runtwo data taking period.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% Standard Model %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Standard Model and the Weak Interaction}
\label{The_Standard_Model}
\input{Chapters/Chapter_1_files/The_Standard_Model}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% Flavor Phisics %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Flavor Physics}
\label{Flavor_Physics}
\input{Chapters/Chapter_1_files/Flavor_Physics}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% The BBbar system%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{The \Bs Meson and \CP violation}
\label{Phenomenology}
\input{Chapters/Chapter_1_files/Bs_phenomenology}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% The BBbar system%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{The Weak Phase $\boldsymbol{\phis}$}
\label{WeakPhase}
\input{Chapters/Chapter_1_files/Weak_Phase}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% The BBbar system%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
