% Chapter 4
\chapter{Data Analysis}
\label{Data_Analysis}

The parameters of interest as described in \chapref{Introduction} {\color{red} section blah} are extracted from the analysis of the
\runone \lhcb data accumulated over the years 2011 and 2012, which correspond to a total integrated luminosity
of 3\invfb. To fit these data a weighted maximum likelihood fit to the angular distributions of \BsJpsiKst is performed,
where the weights have been computed with the \sPlot technique \cite{splot} described in \secref{sWeighting_and_mass}.
Prior to any angular analysis the data as they come straight from the detector need to be filtered to reduce the presence of 
background events. Thus the current chapter addresses first the event selection and then the angular analysis.

\secref{Event_Selection} describes all the steps involved to reduce background in the data. For this purpose
it is necessary to model the $J/\psi K\pi$ invariant mass distribution in the region of the \Bs meson, which
is addressed in \secref{sWeighting_and_mass}. In \secref{Angular_Analysis} the angular analysis is described.\\

% Section Event Selection
\section{Event Selection}
\label{Event_Selection}

There are effectively four stages of offline event selection taking place after the data has been written out. 
First a set of rough pre-selection criteria is applied (hereafter {\it Stripping}). Those cuts are quantities like track and vertex quality {\color{red}(jargon:track and vertex?)},
track impact parameter, mass ranges of mother and daughter particles, particle identification and transverse momentum. A detailed 
table of the Stripping cuts is given in \tabref{Bs2JpsiKstSelection}. The purpose of stripping is to perform a first rough rejection of the combinatorial
background and prepare the data for the next stage of selection \footnote{Stripping is also a way to save disk space for offline event storage, since it is impossible
to save anything that the detector writes out}. The remaining three selection steps after Stripping are described in each of the subsequent subsections.

\input{Chapters/Chapter_4_files/Selection}

% Section Angular Analysis
\section{Angular Analysis}
\label{Angular_Analysis}
 
The core formalistm and all the necessary steps towards build a PDF to describe the angular properties of \BJpsiKst decays are presented in
the current section. The formalism is developed based on the helicity formalism (see next section). A brief discription of 
angular pdf derivation is given in \secref{Diferential_Decay_Rate}. Then in \secref{Kpi_Invariant_mass} the implications arising from the
\mkpi dependance are discussed. Treatment of the angular acceptance are addressed in \secref{Accceptance} and \secref{Accceptance_Corrections}.
Lastly the total decay rate as well as the \ACP parameters of interest are discussed in \secref{Total_Decay_Rate} along with details
on the maximum likeohood fit implementation.

\input{Chapters/Chapter_4_files/Angular_Analysis}

% Section Results
\section{Results}
\label{Results}
\input{Chapters/Chapter_4_files/Results}

% Section Normalization
\section{Normalization of \BsJpsiKpi}
\label{Normalization}
