\chapter*{Acknowledgements}
\chaptermark{}
\addcontentsline{toc}{chapter}{Acknowledgements}

By means of the current thesis I pay tribute to my parents, the two people that always
supported me. Perhaps without even really reliasing themselves, they provided the necesssary conditions
for me to develop both an endless curiosity about everthing around me, and a thirst for the truth,
which are essentially the reasons that I got involved in research. Regarding my nikhef colleques,
Roel Aaij and Jeroen van Leerdam deserve a big and warm thank you. These people always found time to
supported me at the begining of my PhD, asnwering all my questions and guiding me into programming in
a clean and readable way. Special thanks goes to Diego Matines Santos the most clever, modest
and cool scientist I ever worked close with. Furthermore, another person that was always an endless
tunk of knowledge at my disposal is my supervisor, Gerhard Raven. I thank him a lot for his patience
thoroughout my PhD as well as for his time that would always find for me to discuss with him.
I also thank my co-promotor, Patrick Kopenberg, for his detailed review of my thesis (and for
copying with my spelling mistakes). Special thanks also go to the stuff memebers of the nikhef
\lhcb group, and particularly to Marcel Merk, for providing a healthy, full of knowledge and of
course fun working environment. Lastly, I particularly thank my colleques and friends Panagiwti
Tsopela and Jacco de Vries, which I both met at the beggining of my master in 2010. We have
faced the same difficulties and helped each other many times. But above all I thank them for
being kind and fun people, which are not so common features.
